A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-21 article/02_Materials_and_Methods.Rmd
removed colour terms from figure and table captions

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_graves.jpeg}
\caption{\label{map_graves}All graves dating between 2200 and 800calBC as extracted from the Radon-B database (\url{radon-b.ufg.uni-kiel.de}). The classes of the variable \textit{burial type} are distinguished by colour, the ones of \textit{burial construction} by shape. The red frame indicates the research area. The Map projection is EPSG:102013 and the base layer (land, rivers, lakes) data is taken from the Natural Earth project (\url{www.naturalearthdata.com}).}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/sed_region_matrix.jpeg}
\caption{\label{sed_region_matrix}Plot matrix of the region-region squared Euclidean distance time series. In the top right half for the variable \textit{burial type} and in the bottom left for the variable \textit{burial construction}. On the x-axis the time is displayed, on the y-axis the squared Euclidean distance between the two relevant regions. The faint, grey line shows the actual data, the stronger, coloured line an approximation (LOESS with $span = 0.3$).}
\end{figure*}

@@

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
distance_and_correlation_table %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Mean|Correlation")),
    dplyr::funs(kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black"))) 
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    dplyr::funs(kableExtra::cell_spec(., "latex", bold = . < 0.1)) 
  ) %>%
knitr::kable(
  "latex", 
  caption = "Mean distance, correlation and mantel test results for cultural and spatial distance. Listed are the the overall mean squared euclidian distances for each 200 years time slot of all region-region relations and the result statistics of the Mantel test for the variables \\textit{burial type (bt)} (\\textbf{A}) and \\textit{burial construction (bt)} (\\textbf{B}) with the spatial (sp) distance matrix (Figure \\ref{map_regions} B). (\\textbf{C}) shows the Mantel test results for the two variables if compared directly with each other. Negative correlation coefficients are printed red and $p$-values below $0.1$ bold.", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type & spatial distance" = 3, "burial construction & spatial distance" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::add_header_above(
    c(" ", "A" = 3, "B" = 3, "C" = 2),
    bold = T, line = F
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 9,
    full_width = T
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/simulation.jpeg}
\caption{\label{simulation}Development of correlation between cultural and spatial distance for real world data and simulation results. The plots in the left column of the plot matrix (\textbf{ACE}) contain simulation results for an equal group distance matrix $I$, the ones on the right (\textbf{BDF}) for a distance matrix based on the macro unit distances defined for this paper (Figure \ref{map_regions} B). The rows of the plot matrix (\textbf{AB}, \textbf{CD}, \textbf{EF}) represent different degrees of intergroup transmission $m_i$. Each plot shows the results of 50 simulation runs. The x-axis displays the time distinguished into 200 year time slots, the y-axis Spearman's rank correlation coefficient between the mean squared Euclidean distance matrix for a 200 year time slot and the static spatial distance matrix. This information is visualized for each time slot with (from left to right) a dotplot coloured according to the $p$-value of the Mantel test, a scatter plot line and a boxplot. The scatter plot points of one simulation run are connected with a faint line from one time slot to the next. To compare the runs with the real world observations, the results for the burial customs data (Table \ref{tab:distanceandcorrelationtable*} AB) is added here with with a stronger green and blue line. The strong horizontal red line marks the correlation coefficient of zero, where neither positive nor negative correlation can be assumed.}
\end{figure*}

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_graves.jpeg}
\caption{\label{map_graves}All graves dating between 2200 and 800calBC as extracted from the Radon-B database (\url{radon-b.ufg.uni-kiel.de}). The classes of the variable \textit{burial type} are distinguished by colour, the ones of \textit{burial construction} by shape. The rectangular frame indicates the research area. The Map projection is EPSG:102013 and the base layer (land, rivers, lakes) data is taken from the Natural Earth project (\url{www.naturalearthdata.com}).}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/sed_region_matrix.jpeg}
\caption{\label{sed_region_matrix}Plot matrix of the region-region squared Euclidean distance time series. In the top right half for the variable \textit{burial type} and in the bottom left for the variable \textit{burial construction}. On the x-axis the time is displayed, on the y-axis the squared Euclidean distance between the two relevant regions. The faint line shows the actual data, the stronger line an approximation (LOESS with $span = 0.3$).}
\end{figure*}

@@

```{r distanceandcorrelationtable, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/distance_and_correlation_table.RData")
distance_and_correlation_table %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("Mean|Correlation")),
    dplyr::funs(kableExtra::cell_spec(., "latex", color = ifelse(. < 0, "red", "black"))) 
  ) %>%
  dplyr::mutate_at(
    dplyr::vars(dplyr::matches("p-Value")),
    dplyr::funs(kableExtra::cell_spec(., "latex", bold = . < 0.1)) 
  ) %>%
knitr::kable(
  "latex", 
  caption = "Mean distance, correlation and mantel test results for cultural and spatial distance. Listed are the the overall mean squared euclidian distances for each 200 years time slot of all region-region relations and the result statistics of the Mantel test for the variables \\textit{burial type (bt)} (\\textbf{A}) and \\textit{burial construction (bt)} (\\textbf{B}) with the spatial (sp) distance matrix (Figure \\ref{map_regions} B). (\\textbf{C}) shows the Mantel test results for the two variables if compared directly with each other. $p$-values below $0.1$ are printed bold.", 
  booktabs = T,
  linesep = "\\addlinespace \\hline \\addlinespace",
  escape = F
) %>%
  kableExtra::add_header_above(
    c(" ", "burial type & spatial distance" = 3, "burial construction & spatial distance" = 3, "variable correlation" = 2)
  ) %>%
  kableExtra::add_header_above(
    c(" ", "A" = 3, "B" = 3, "C" = 2),
    bold = T, line = F
  ) %>%
  kableExtra::kable_styling(
    latex_options = c("hold_position"),
    font_size = 9,
    full_width = T
  ) %>%
  kableExtra::column_spec(c(2,4,5,7,9), width = "1.2cm") %>%
  kableExtra::column_spec(c(3,6,8), width = "1.8cm") %>%
  gsub("table", "table*", .)
```

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/simulation.jpeg}
\caption{\label{simulation}Development of correlation between cultural and spatial distance for real world data and simulation results. The plots in the left column of the plot matrix (\textbf{ACE}) contain simulation results for an equal group distance matrix $I$, the ones on the right (\textbf{BDF}) for a distance matrix based on the macro unit distances defined for this paper (Figure \ref{map_regions} B). The rows of the plot matrix (\textbf{AB}, \textbf{CD}, \textbf{EF}) represent different degrees of intergroup transmission $m_i$. Each plot shows the results of 50 simulation runs. The x-axis displays the time distinguished into 200 year time slots, the y-axis Spearman's rank correlation coefficient between the mean squared Euclidean distance matrix for a 200 year time slot and the static spatial distance matrix. This information is visualized for each time slot with (from left to right) a dotplot coloured according to the $p$-value of the Mantel test, a scatter plot line and a boxplot. The scatter plot points of one simulation run are connected with a faint line from one time slot to the next. To compare the runs with the real world observations, the results for the burial customs data (Table \ref{tab:distanceandcorrelationtable*} AB) is added here with with a stronger solid (\textit{burial type}) and dashed (\textit{burial construction}) line. The strong horizontal line marks the correlation coefficient of zero, where neither positive nor negative correlation can be assumed.}
\end{figure*}
